---
title: "BEST-Damingshan"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>

## Mt. Damingshan (广西大明山)

Damingshan is located in Guangxi Province.

<div align="center">
```{r DT, echo=FALSE, message=FALSE, warning=FALSE}
# example: https://www.earthdatascience.org/courses/earth-analytics/get-data-using-apis/leaflet-r/
library(dplyr)
library(ggplot2)
library(rjson)
library(jsonlite)
library(leaflet)
library(RCurl)
library(openxlsx)
dat <- read.xlsx("I:\\Research\\BEST\\BEST_Documents\\Locations_Best_Current.xlsx")
dat <- dat[which(dat$Name=="Damingshan"),]
best_map <- leaflet() %>%
  addProviderTiles("Esri.NatGeoWorldMap") %>%
  addCircleMarkers(color = "red", stroke = FALSE, fillOpacity = 0.5, lng=dat$long, lat=dat$lat, popup=dat$Name2)%>%
  setView(dat$long[1], dat$lat[1], zoom = 8)
best_map
```
</div>

<hr>

### **Vegetation**

Coming soon.

<hr>

### **Flora**

Coming soon.

<hr>

### **Fauna**

Coming soon.

<hr>

### **Research sites of BEST network**

Coming soon.

<hr>

### **Principal Investigator**

Gang Hu (胡刚): [ahhugang@126.com](mailto:ahhugang@126.com)

**Research Team**:

-  Dr. Yinghua Luo (Guangxi University)


<hr>

### **Selected Publications**

Coming soon.

<hr>

### **Site Support**

This site has been supported by:

-   Damingshan National Nature Reserve

<hr>